asdfasf

### 2021-11-26 src/ms.tex
bug fix
add fig to paper

GRBs are transient sources with a typical duration only up to a few tens of seconds.
%Therefore we can use the time before and after the GRB signal, but within the same science window, as a background measurement.
%The background treatment we use, depends on two assumptions, namely that within one science window the background is stable and the pointing direction of SPI does not change.
%Due to the high orbit and pointing scheme of INTEGRAL both these assumptions are valid.
Therefore we can use the time intervals during a science window when the transient source is not active as an independent background measurement. Similar to other instruments that use spatially off-source observation as an independent background measurement. In the case of transients in SPI we have temporal off-source observation. From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
\begin{equation}
	L(b_{i}|B_{i}, t_{b})=\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
  \label{eq:poisson_bkg}
\end{equation}
This will be used in the next paragraph to derive the total likelihood.
% add a lightcurve plot?

@@

Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation. For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum should be zero. Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m(\theta)_{i}$ and observed counts. Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
\begin{equation}
	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)}(t_{b}+t_{d})+\sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
  \label{eq:bmax}
\end{equation}

>>>>

GRBs are transient sources with a typical duration only up to a few tens of seconds.
%Therefore we can use the time before and after the GRB signal, but within the same science window, as a background measurement.
%The background treatment we use, depends on two assumptions, namely that within one science window the background is stable and the pointing direction of SPI does not change.
%Due to the high orbit and pointing scheme of INTEGRAL both these assumptions are valid.
Therefore we can use the time intervals during a science window when the transient source is not active as an independent background measurement. Similar to other instruments that use spatially off-source observation as an independent background measurement. In the case of transients in SPI we have temporal off-source observation (see Fig. \ref{fig:lightcurve}). From the background observations we construct the probability of the background model rates per energy channel from a poisson distribution, like given in equation \ref{eq:poisson_bkg}, where $b_{i}$ are the background rates per energy channel, $B_{i}$ are the detected counts in the off-source observation and $t_{b}$ is the exposure of the off-source observation.
\begin{equation}
	L(b_{i}|B_{i}, t_{b})=\frac{(t_{b} b_{i})^{B_{i}}}{B_{i}!}\cdot e^{-t_{b} b_{i}}
  \label{eq:poisson_bkg}
\end{equation}
This will be used in the next paragraph to derive the total likelihood.

\begin{figure}
    \begin{centering}
        \includegraphics{figures/lightcurve.pdf}
        \caption{Lightcurve for SPI detector 0 for GRB120711A. The transient source is clearly visible as well as the constant background for the time when the transient is not active.}
        % This label tells showyourwork that the script `figures/mandelbrot.py'
        % generates the PDF file included above
        \label{fig:lightcurve}
    \end{centering}
\end{figure}

% add a lightcurve plot?

@@

Because there is no easy analytical solution for this integral, one often uses a so-called profiled likelihood as an approximation. For the profiled likelihood we use the fact, that the derivative of the likelihood at its maximum should be zero. Therefore one can construct from $\frac{\textrm{dL}}{\textrm{db}_i}=0$ the background rates $b_{i, max}$ that maximize the likelihood for a given model $m(\theta)_{i}$ and observed counts. Solving $\frac{\textrm{dL}}{\textrm{db}_i}=0$ for b gives equation \ref{eq:bmax}.
\begin{equation}
	b_{i,max}(\theta)=\frac{1}{2(t_{b}+t_{d})}(B_{i}+D_{i}-m_{i}(\theta)(t_{b}+t_{d})+\sqrt{(B_{i}+D_{i}+m_{i}(\theta)(t_{b}+t_{d}))^{2}-4m_{i}(\theta)D_{i}(t_{d}-t_{b})}
  \label{eq:bmax}
\end{equation}
